---
output:
  md_document:
    variant: markdown_github
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  error = TRUE
)
```

# tgconfig

The goal of tgconfig is to provide infrastructure for managing package parameters. 

Parameters are easy to get in relevant functions within a package:

```{r example}
library(tgconfig)
register_param('param', 'scrdb')
set_param('param', 'value', 'scrdb')
get_param_strict('param', 'scrdb')
```

Error is thrown if a parameter is missing:
```{r}
get_param_strict('another', 'scrdb')
```

Developers are able to register parameters and set their default value in a config file that is part of the package in YAML format:

```{yaml}
char_param: value
expr_param: !expr seq(1:5)
numeric_param: 500
boolean_param: true
```

```{r}
config_file <- example_config_file()
register_params(config_file, 'scrdb')
get_package_params('scrdb')
```

Users are able to override parameters using their own YAML:
```{r}
override_params(system.file('config/override_example.yaml', package='tgconfig'), package='scrdb')
get_package_params('scrdb')
```

Users get an exception when trying to override a parameters that was not registered:

```{r}
set_param('other_param', 'value', 'scrdb')
```

